Chronic conditions and increased antibiotic consumption

### 2017-03-28 chronic-conditions/chronic-condition-drivers.Rmd
negative binomial

>>>>

### Negative binomial

The claims data are distributed more like a negative binomial than a Poisson (i.e., the variance in counts exceeds the mean). Negative binomial regressions give similar results to the Poisson results. For example, the COPD coefficient is 0.811 (vs. 0.806) and the rheumatoid arthritis coefficient is 0.466 (vs. 0.465).

```{r negative_binomial}
usage %>%
  mutate(age=age-65) %>%
  MASS::glm.nb(n_claims ~ age + is_female + COPD, data=.) %>%
  broom::tidy %>%
  select(term, estimate)
```
